### 2019-11-14 README.Rmd
Add Github actions to test

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/llrs/experDesign.svg?branch=master)](https://travis-ci.org/llrs/experDesign)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/llrs/experDesign?branch=master&svg=true)](https://ci.appveyor.com/project/llrs/experDesign)
[![Coverage status](https://codecov.io/gh/llrs/experDesign/branch/master/graph/badge.svg)](https://codecov.io/github/llrs/experDesign?branch=master)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
<!-- badges: end -->

@@

This is a basic example which shows you how to solve a common problem:

```{r design}
library("experDesign")
metadata <- expand.grid(height = seq(60, 80, 5), 
                        weight = seq(100, 300, 50),
                        sex = c("Male","Female"))
head(metadata, 15)
d <- design(metadata, 24)
# It is a list but we can convert it to a vector with:
batch_names(d)

```

Naively one would either fill some batches fully or distribute them not evenly 
(the  first 17 packages toghether, the next 17 and so on). This solution ensures 
that the data is randomized.

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/llrs/experDesign.svg?branch=master)](https://travis-ci.org/llrs/experDesign)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/llrs/experDesign?branch=master&svg=true)](https://ci.appveyor.com/project/llrs/experDesign)
[![Coverage status](https://codecov.io/gh/llrs/experDesign/branch/master/graph/badge.svg)](https://codecov.io/github/llrs/experDesign?branch=master)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![R build status](https://github.com/llrs/experDesign/workflows/R-CMD-check/badge.svg)](https://github.com/llrs/experDesign/actions?workflow=R-CMD-check)
<!-- badges: end -->

@@

Imagine you have some samples already collected and you want to distributed them in batches:
```{r experDesign_setup}
library("experDesign")
metadata <- expand.grid(height = seq(60, 80, 5), 
                        weight = seq(100, 300, 50),
                        sex = c("Male","Female"))
head(metadata, 15)
```

If you block incorrectly and end up with a group in a single batch we will end up with batch effect.
In order to avoid this `design` helps you assign each sample to a batch (in this case each batch has 24 samples at most.):

```{r design}
d <- design(metadata, 24)
# It is a list but we can convert it to a vector with:
batch_names(d)
```

Naively one would either fill some batches fully or distribute them not evenly 
(the  first 17 packages together, the next 17 and so on). This solution ensures 
that the data is randomized.
